Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
removed addressed todo on de-vectorization in sec 4.5
"proof" for stability being independent of FWL error - not sure this is right

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .  \forall x.  \sigma(x, P)$ 
where $P$ ranges over functions, $x$ 
 ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

\begin{enumerate}
\item 
We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
% Let us recall the formulas used for single-input and single-output (SISO) systems 
% in sections \ref{sec:reachable} and \ref{sec:observable}.
A controllable system with quantization will have the following dynamics 
(note that we use underscript ``n'' to denote a noise term and
``cf'' to denote Controllable Canonical Form):
\todo{eliminate vectors}
%
\begin{align}
\label{eq:observer_LTI_cf}
x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
\end{align}
\begin{align*}
\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
\mat{B}_{t}=&\mat{T}\mat{B}_d&
\mat{B}_{n}=&[1 \cdots 1]^T&
\mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
\end{align*}

@@

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .  \forall x.  \sigma(x, P)$ 
where $P$ ranges over functions, $x$ 
 ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

\begin{enumerate}
\item 
We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
% Let us recall the formulas used for single-input and single-output (SISO) systems 
% in sections \ref{sec:reachable} and \ref{sec:observable}.
A controllable system with quantization will have the following dynamics 
(note that we use underscript ``n'' to denote a noise term and
``cf'' to denote Controllable Canonical Form):
%\todo{eliminate vectors}
%
\begin{align}
\label{eq:observer_LTI_cf}
x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
\end{align}
\begin{align*}
\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
\mat{B}_{t}=&\mat{T}\mat{B}_d&
\mat{B}_{n}=&[1 \cdots 1]^T&
\mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
\end{align*}

@@

%-------------------------------
\subsection{Stability of closed-loop systems with fixed-point controller error}
%-------------------------------

The proof above relies on the fact that the relationship between states and next states is defined by
$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
the operation becomes:
\begin{align*}
x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once. We derive the closed form expression for $x_n$

\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{k+1} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
\end{align*}

The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
reference signal so an asymptotically stable system will converge to the origin. We know that the original system
with an infinite precision controller is stable, because we have synthesised it to meet Jury's criteria. Hence
$(A_d  - B_dK)^n*x_0$ must converge to zero.

Hence, we can show that a fixed point implementation of the same controller will converge to a steady value, as 
all terms that contain $(A_d  - B_dK)^k$ will eventually converge to zero, and the remaining non-converging term is $B_dK\delta$.

We do not require asymptotic stability to ensure safety, we do require that the controller converges to a steady value 
in the safe state values.
